### 2021-05-26 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Fix latex compile issue with pdfs (#8)
* Remove scalebox before \includegraphics

* Add updated .pdf

* Chnage the way pdf compiles in CI

tasks.py are updated so that latexmk runs with the xelatex parameter

* Update CI to install additional libraries

Specifically: texlive-xetex, texlive-science

* Restructure imgs/ directory
Add new violinplots
Include violin plots of performance measures over
different values of lambda_2 for type 1, type 2 and
overall individuals

>>>>

Additional details on the blocking time formula 
(\ref{eq:algebraic_blocking_time}) can be found in appendix 
\ref{sec:appendix_mean_blocking}.

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation.
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\)

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/blocking_time_comparison/blocking.pdf}
    \caption{
        Comparison of mean blocking time between values obtained from the Markov 
        chain formulas and values obtained from simulation.
    }
    \label{fig:markov_vs_des_blocking_time_comparison}
\end{figure}

### 2021-05-26 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Fix latex compile issue with pdfs (#8)
* Remove scalebox before \includegraphics

* Add updated .pdf

* Chnage the way pdf compiles in CI

tasks.py are updated so that latexmk runs with the xelatex parameter

* Update CI to install additional libraries

Specifically: texlive-xetex, texlive-science

* Restructure imgs/ directory
Add new violinplots
Include violin plots of performance measures over
different values of lambda_2 for type 1, type 2 and
overall individuals

>>>>

Appendix \ref{sec:appendix_mean_waiting} gives more details on the recursive
formula that equations (\ref{eq:closed_form_waiting_type_1}),
(\ref{eq:closed_form_waiting_type_2}) and (\ref{eq:overall_waiting_time})
originate from.

Figures \ref{fig:markov_vs_des_waiting_time_comparison_1},
\ref{fig:markov_vs_des_waiting_time_comparison_2} and
\ref{fig:markov_vs_des_waiting_time_comparison_overall} show a comparison 
between the calculated mean waiting time using Markov chains and the simulated 
waiting time using discrete event simulation over a range of values of 
\(\lambda_2\).
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_1.pdf}
    \caption{
        Comparison of mean waiting time for type 1 individuals between values 
        obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_2.pdf}
    \caption{
        Comparison of mean waiting time for type 2 individuals between values 
        obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_2}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_overall.pdf}
    \caption{
        Comparison of mean waiting time for both types of individuals between 
        values obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_overall}
\end{figure}

% TODO: Possibly add another example that will be used in section 5
